Review questions list

### 2020-10-15 docs/revision/reply.tex
replied: reviewer 2 :: reviewer 3 except last Q

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

	\hl{We would to thank the respected reviewer for his sharpness. We have reread the manuscript and corrected spelling errors as well as grammatical errors, as much as we could. }

@@

	\hl{Though the respected reviewer makes a valid point regarding data augmentation techniques, however, our study was not comparative in nature, thus, other data augmentation techniques will be investigated in future work. Furthermore, we have chosen GAN due to its effectiveness and popularity, as we the references we provided demonstrate.}

@@

	\hl{By using [18] as a starting point and carrying systematic experimentations, the ANN architecture was structured as the one which stabilized the loss curve and general enough to have acceptable validation errors on both data sets.}

@@

	\hl{We would like to thank the reviewer for noticing the ill defined Table. Yes, the metric is the MSE, as shown in the tilte of Table II in the new manuscript.}

@@

	\hl{We very much appreciate the reviewer's remark on the missing the full form of RI. RI referes to the Refractive Index as it is indicated in the same line in the new manuscript. }

@@

	\hl{During our experiments we used part of the data to validate training. In an attempt to stay within the maximum page limits, we had decided to not include the validation curves.
	 The ANN's performance on the validation is provided in Figure 4 in the new manuscript.}

@@

	\hl{The requested MSEs are provided on the graphs in the new manuscript.} \\
	\textcolor{red}{AZ: CK Should we discuss the MSEs here? I think you provided the same answer for Reviewer 1 - Q5.}

@@

	\hl{We strongly agree with the reviewer's valuable suggestion. In fact the very reason that propelled us to choose WGAN is its stopping criteria. The loss curve of the WGAN converges in a stable manner indicating the end of the training phase, as it measures the distance between the distrubutions of real and generated data, which in return, to a high degree of certainty - probabilistically speaking-, validates our generated data. Due to the number of pages limitation, we decided not to include the loss graph of the WGAN, however, experiments showed that the curve converges in a stable manner to 0.}

@@

	\hl{For the purpose of saving space we have not included the corresponding table, which includes detailed information about the data sets. 
	For the SPR set,  for the 9 folds, we used 336 samples to train the GAN and the ANN, 48 for validation and 48 for testing. Please note that each geometric configuration has 16 data point per analyte making up to 48 for the 3 analytes used.
	For the PCF set: for the 10 folds, we used about 10$\%$ for testing, about 10$\%$ for validation and the rest for training the ANN and GAN.}

@@

	\hl{The importance of real data dilutes as the number of generated data increases, thus, there is a balance to strive for. To support our claim we conducted further experiments and added the correspoding MSEs to the bar chart of Fugure 6.}
